MaxEnt: What is it good for?

### 2015-06-19 ms.tex
New section and some more words

Throughout this article I will present, but not derive or prove, MaxEnt
results for certain types of testable information.

@@

@@

>>>>

Throughout this article I will present, but not derive or prove, MaxEnt
results for certain types of testable information. Some of these are well
known (e.g. the expected value constraints discussed in
Section~\ref{sec:expected_values}) while others are less so.

@@

This has led to the widespread (and in my view, incorrect) belief that
MaxEnt and Bayesian inference are ``incompatible'', and the

@@

\subsection{Skilling's criticism}
Skilling thinks this is ``deriving Bayes again, when it's already there
as the product rule''. I consider it more as a demonstration of which
particular constraints are epistemically equivalent to learning the
truth of a propositions. It turns out to be the rather obvious constraint
that the probability we should assign to a proposition we know to be true
is 1.

I also think this viewpoint clarifies thinking about the ``probability
distribution for the data'' (interpretation of sampling distributions etc).
